Search techniques for gaussian mixture modelling with Minimum Message Length, with applications to the origin of our Galaxy

### 2018-10-30 article/ms.tex
track paths

>>>>

\begin{figure}
    \includegraphics[width=1.0\textwidth]{paths-splits.pdf}
    \caption{The number of split operations performed by the benchmark method
             \cite{Kasarapu|Allison:2015} on the top four components (by message
             length) from 169 generated data sets. The \emph{Message-Breaking
             Method} always splits the component with the largest message length.
             Although the benchmark method tries to split, merge, and delete all
             components, it most frequently decides to split the same component
             that the \emph{Message-Breaking Method} splits -- without trialling
             all operations. The benchmark method chose to split (instead of
             merge or delete) in all 2029 operations.}
    \label{fig:path-operations}
\end{figure}
